\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\renewcommand{\baselinestretch}{1.5}
\newcommand{\sq}{\scalebox{1.5}{$\square$}}
%\title{}
%\date{}
\begin{document}
%%
\pagestyle{empty}
%\maketitle
\begin{center}
	\Large{\textbf{Self-certification for the ED5603: Project-III \\Mid-semester progress report}}
\end{center}
%%
\vspace{1 cm}
%%
\noindent Please tick the check-boxes appropriately and confirm the same via your signature (with the date of submission of the report) at the bottom of the page. 
%%
\begin{itemize}
    \item[\sq] All the figures and tables have their individual captions.
	\item[\sq] Sources for all the figures, tables etc. which have not been created by the author (e.g., taken from another report or a paper/book) have been mentioned in the respective captions.
	\item[\sq] All symbols denoting various variables, parameters, etc. have been clearly defined when they are being introduced in the text.
	\item[\sq] Any given symbol retains the same meaning and appearance (i.e., font type, size, style, etc.) all through the document.
	\item[\sq] All the numeric entities presented in the report use the same number of digits after the decimal, unless mentioned otherwise.
	\item[\sq] Units for all the physical entities/variables appearing in the report have been mentioned clearly.
	
	\item[\sq] All the figures and tables have been referred to in the main text.
	\item[\sq] The axis-labels, legends (wherever appropriate) have been added to all the figures.
	\item[\sq] All the text elements, e.g., labels, text in the legends, etc. are clearly legible.
	\item[\sq] An automated spelling-check has been done using the software \rule{5 cm}{0.1 mm}, following the \rule{5 cm}{0.1 mm} (e.g., English UK/US/India) dictionary.
	\item[\sq] An automated grammar-check has been done using the software \rule{5 cm}{0.1 mm} (e.g., MS Word, Grammarly) following the same dictionary as above. 
\end{itemize}
%%
\vspace{1 cm}
%%
Roll number: \hfill Name: \hspace{5 cm} \\

\vspace{1.5 cm}
\noindent Signature of the student: \hfill Date: \hspace{5 cm}
%%
\end{document}
